---
title: "Music Insights"
author: "Robert Ramos"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

First, we need tidyverse to handle data importing and wrangling
(when uploading csv file avoid absolute paths, use relative paths)
```{r}
#install.packages("tidyverse")
library("tidyverse")
library("readr")
library("ggplot2")

survey<-read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences<-read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")


nrow(survey)
colnames(survey)


nrow(preferences)
colnames(preferences)
```

Cleaning survey data frame column names
```{r}
colnames(survey)[colnames(survey)=="First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"]<-"generator_name"

colnames(survey)[colnames(survey)=="What is your pseudonym?"]<-"pseudonym"

colnames(survey)[colnames(survey)=="Year you were born (YYYY)"]<-"Birth_Year"

colnames(survey)[colnames(survey)=="Which musical instruments/talents do you play? (Select all that apply)"]<-"Musical_Talents"

colnames(survey)[colnames(survey)=="Link to song (on Youtube or Vimeo)"]<-"Link"
```

This is when I make 2 tables, one for Person and one for FavoriteSong.
```{r}
library("dplyr")
library("tidyr")

Person<-tibble(pseudonym = survey$pseudonym, generator_Name = survey$generator_name, Sex = survey$Sex, major = survey$Major, AcademicYear = survey$"Academic Year", Birth_Year = survey$Birth_Year)

Person$AcademicYear<-as.factor(Person$AcademicYear)
Person$major<-as.factor(Person$major)

levels(Person$major)[levels(Person$major) =="Computer information Systems"] <- "Computer Information Systems"


FavoriteSong<-tibble(Pseudonym = survey$pseudonym, Song = survey$Song, Artist = survey$Artist, Link = survey$Link)


preferences<-gather(preferences,Artist_Song, rating, 3:45)

Ratings<-tibble(Pseudonym = preferences$"What was your pseudonym?", Artist_Song = preferences$Artist_Song, Ratings = preferences$rating)


ggplot(Ratings, aes(x = Ratings) ) + geom_histogram(binwidth = 1)
ggplot(Ratings, aes(x = Ratings, y = Pseudonym)) + geom_bin2d() #+scale_x_discrete(limits = c())
```


```{r}
survey$Timestamp<-as.POSIXlt(parse_datetime(as.character(survey$Timestamp),format = "%y/%m/%d %H:%M:%S"))

```


```{r}
a<-inner_join(FavoriteSong, Ratings, by = "Pseudonym")
a
##Left- only people who provided their favorite song
##Right- only people who provided ratings
##Full- Everyone, but possible missing "matches"
##Inner- only people who provided both their song and the ratigns for the songs
 
```

For people who gave more than 1 response, this is to get the earlier ratings
```{r}
#earliest_time<-min(preferences$Timestamp)##Not finished


```

Now this section will fix the naming so it can read tabs and spaces
```{r}
Ratings$Artist_Song<- str_replace_all(Ratings$Artist_Song,
                                      pattern = "\t",
                                      replacement = " ")

favorite_rating <- Ratings %>%
  left_join(FavoriteSong, by = "Pseudonym") %>%
  filter(Artist_Song == paste(Artist,Song)) %>%
  select(Pseudonym, Artist_Song,Ratings)

print(favorite_rating)

```
